Clicks and Cliques

### 2018-12-22 papersoul.Rnw
life_seq chunk from qplot to ggplot

# levels(soul$Q5)[1:2] <- 'Non Response'
# levels(soul$Q5)[2:6] <- 'Move from your neighborhood'
# soul$Q5 <- factor(soul$Q5)

# pr <- with(subset(soul, !is.na(PROJWT) ), PROJWT/3)
# des.pro <- svydesign(ids=~1, strata=~QSB, weights=~pr, data=subset(soul, !is.na(PROJWT) ) )
# tab <- svyby(~Q5,~CCEGRP2, des.pro, svymean,keep.var=FALSE, na.rm=T)
# tab <- round(100*ftable(tab), 2)
# dt <- data.frame(matrix(tab[1:9], ncol=3))
# rownames(dt) <- levels(soul$Q5)
# colnames(dt) <- levels(soul$CCEGRP2)
# dt <- xtable(dt, caption='Willingness to move outside your neighborhood', label='move')
# print(dt, caption.placement='top')

@@

\begin{figure}
<<life_seq, dependson=c('life'), echo=FALSE,fig.height=4,message=FALSE,warning=FALSE>>=
life$QSB <- with(life, factor(QSB, levels = rev(levels(QSB))))

lifevar %>% data.frame() %>%  select(-starts_with('se')) %>%
  qplot(data=., x=QSB,ymax=rho,ymin=0, xlab='',geom='linerange', ylab='Correlation',size=I(2))  + theme(axis.text.y = element_text( size=I(10) ),axis.text.x = element_text(size=I(10), angle=90),axis.title.x = element_text(size=I(25)))
@
\caption{ Bar chart of correlations between attachment and lifetime living in the community within each community (ordered by attachment level). Only few communities shows negative correlation between attachment and lifetime living there. \label{wrho}}
\end{figure}

>>>>

@@

\begin{figure}
<<life_seq, dependson=c('life'), echo=FALSE,fig.height=4,message=FALSE,warning=FALSE>>=
# life$QSB <- with(life, factor(QSB, levels = rev(levels(QSB))))
life %<>% life %>%
  mutate(QSB = factor(QSB, levels = rev(levels(QSB))))

lifevar %>% data.frame() %>%  select(-starts_with('se')) %>%
  ggplot(data =., x=QSB,ymax=rho,ymin=0, xlab='',geom='linerange', ylab='Correlation',size=I(2))  + theme(axis.text.y = element_text( size=I(10) ),axis.text.x = element_text(size=I(10), angle=90),axis.title.x = element_text(size=I(25)))
@
\caption{ Bar chart of correlations between attachment and lifetime living in the community within each community (ordered by attachment level). Only few communities shows negative correlation between attachment and lifetime living there. \label{wrho}}
\end{figure}
